---
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
  number_sections: true
 
title: "ISBN Linking"
author: "[User-764Q](https://github.com/User-764Q)"
date: "`r paste0('Last Run: ', format(Sys.time(), '%A %d-%B-%Y'))`"
params: 
  param1: "Don't Forget about params"

---

<style>

#TOC {
 font-family: Calibri; 
 font-size: 16px;
 border-color: #3D68DF;
 background: #3D68DF;
}

body {
  font-family: Garamond;
  font-size: 16px; 
  border-color: #D0D0D0;
  background-color: #D0D0D0;
  color: #1A1A1A;
}

pre {
  color: #1A1A1A
  background: #D0D0D0;
  background-color: #D0D0D0
  font-family: Calibri; 
  
}

</style>

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(collapse = TRUE)

knitr::opts_chunk$set(warning = TRUE)

knitr::opts_chunk$set(message = TRUE)

knitr::opts_chunk$set(include = TRUE)

custom_black <- '1A1A1A'
custom_white <- 'C0C0C0'
custom_grey_dark <- '6F6F6F'
custom_grey_light <- 'B2B2B2'
custom_accent_blue <- '3D6BFF'

```

### Intro/summary 

[Previously](https://github.com/User-764Q/ISBNS_and_Wikibooks) I extracted ISBNs from a wikibooks data set [hosted on Kaggle](https://www.kaggle.com/dhruvildave/wikibooks-dataset), In this project I want to link those ISBNs to existing data sources to add high quality metadaata to the books. 

```{r libraries etc., message = FALSE }

library(tidyverse)

```

```{r dataload}



```

# Heading 1 

## Sub Heading 1

### Sub Sub Heading 1

```{r }

```

